Industrial Applications of CFD

### 2011-03-10 MSTE_methodology.tex
teniamos 2 numerical results, quite 1, ahora tenemos una seccion results. Meti nariz

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{#1} \\}

@@

@@

In this manner, the norm equivalent functional is defined as follows:

\begin{eqnarray} 
\mathcal{J}(\mathbf{f})\equiv  \frac{1}{2}\parallel \mathcal{L} \mathbf{f} -\mathbf{g} \parallel_{Y(\Omega)}^2 + \frac{1}{2} \parallel \mathcal{B}\mathbf{f} - \mathbf{f}_{\Gamma} \parallel_{Y(\Gamma)}^2 
\label{eq:WeakLSQ}
\end{eqnarray}

This functional is a measure of the residual of an aproximating function $\mathbf{f}\in X(\Omega)$.
The residual of the boundary equations is included in equation \ref{eq:WeakLSQ} to allow a weak imposition of the boundary conditions. That is, we allow the use of spaces $X(\Omega)$ that are not constrained to satisfy these conditions.

It is assumed that the problem is well-posed and that the operators $\mathcal{L}$ and $\mathcal{B}$ conform a continuous mapping of the function space $X(\Omega)\times X(\Gamma)$ on the space $Y(\Omega) \times Y(\Gamma)$. Under these conditions, a norm equivalence between the norm of the residual and the norm of the error is established. That is, finding a function $\mathbf{f}\in X(\Omega)$ that minimizes the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding the approximating function in $X(\Omega)$ which is closest to the exact solution to the problem.

@@

\subsection{Solution procedure}
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

\section{Numerical examples}
\textcolor{blue}{Presentar el modelo}

\begin{eqnarray}
\mathbf{L}&=&\mathbf{C_1}\mathbf{Dz}+\mathbf{C_2}\mathbf{H}-\mathbf{I_h} \\
\mathbf{G}&=&\mathbf{S}
\end{eqnarray}

\noindent where $\delta_{qj}$ is the Kronecker delta. The other matrices, namely $\mathbf{H}$, $\mathbf{D_z}$, and $\mathbf{I_h}$ are called operator matrices.

\begin{eqnarray}
\left[\mathbf{I_h}\right]_{qj}&=&\int h(z_q,\xi_q\rightarrow\hat{\xi})\varphi_j(z_q,\hat{\xi}) d\hat{\xi}\nonumber \\
&=&\sum_k h(\xi_q\rightarrow s_k \rightarrow\xi_q)\varphi_j(z_q,s_k) \omega_k
\end{eqnarray}

Here, we define new quadrature points and weights such that $s_k$ exists within the integration boundaries for each row of the integral operator matrix.

\section{Numerical Example}

@@

\noindent with A=, V=, M= and M= \TODO{no me acuerdo}.

>>>>

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{#1} \\}
\newcommand{\Pablo}[1]{\textcolor{blue}{#1}}

@@

\begin{eqnarray}
\mathcal{L} \phi = \mathbf{g} \quad \mbox{in} \ \Omega \label{eq:Problem} \\
\mathcal{B} \phi = \mathbf{f_\Gamma} \quad \mbox{on} \ \Gamma \label{eq:Boundary}
\end{eqnarray}

@@

In this manner, \Pablo{a} norm equivalent functional \Pablo{can} defined as follows:

\begin{eqnarray} 
\mathcal{J}(\mathbf{f})\equiv  \frac{1}{2}\parallel \mathcal{L} \mathbf{f} -\mathbf{g} \parallel_{Y(\Omega)}^2 + \frac{1}{2} \parallel \mathcal{B}\mathbf{f} - \mathbf{f}_{\Gamma} \parallel_{Y(\Gamma)}^2. 
\label{eq:WeakLSQ}
\end{eqnarray}

\begin{eqnarray} 
\mathcal{J}(\mathbf{\bullet})\equiv  \frac{1}{2}\parallel \mathcal{L} \bullet -\mathbf{g} \parallel_{Y(\Omega)}^2 + \frac{1}{2} \parallel \mathcal{B}\bullet - \mathbf{f}_{\Gamma} \parallel_{Y(\Gamma)}^2. 
\label{eq:WeakLSQ3}
\end{eqnarray}

\Pablo{The functional $\mathcal{J}(\mathbf{f})$} is a measure of the residual of an aproximating function $\mathbf{f}\in X(\Omega)$.
The residual of the boundary equations is included in equation \ref{eq:WeakLSQ} \Pablo{(second term of the RHS)} to allow a weak imposition of the boundary conditions. That is, we allow the use of spaces $X(\Omega)$ that are not constrained to satisfy these conditions.

It is assumed that the problem is well-posed and that the operators $\mathcal{L}$ and $\mathcal{B}$ conform a continuous mapping of the function space $X(\Omega)\times X(\Gamma)$ on the space $Y(\Omega) \times Y(\Gamma)$ \Pablo{EEEEhh.... quien es Y?}. Under these conditions, a norm equivalence between the norm of the residual and the norm of the error is established. That is, finding a function $\mathbf{f}\in X(\Omega)$ that minimizes the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding the approximating function in $X(\Omega)$ which is closest to the exact solution to the problem.

\Pablo{Yo lo entiendo porque yo se LSQ (algo al menos)... pero no se como se explica mejor realmente... $\mathbf{f}$ es la solucion o es la aproximacion a la solucion? equacion 2 es inconsistente con el resto... o no? Es una muy poco feliz decision elegir el mismo symbolo para ambas, o no? Debido a que en nuestro problema la solucion es $\phi$ decidi hacer el cambio en la definicion del problema. Luego usamos $\mathbf{f}$ para la aprox solo.  Agregue un texto que capaz ayuda para aclarar ese punto.}

@@

\subsection{Solution procedure}

\TODO{No he leido esta seccion todavia}
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

\section{Numerical examples}

@@

We rewrite the problem equation \ref{eq:ss2} as,

\begin{eqnarray}
\mathbf{L}&=&\mathbf{C_1}\mathbf{Dz}+\mathbf{C_2}\mathbf{H} \Pablo{+} \mathbf{I_h} \\
\mathbf{G}&=&\mathbf{S}
\end{eqnarray}

\noindent where $\delta_{qj}$ is the Kronecker delta. The other matrices, namely $\mathbf{D_z}$, $\mathbf{H}$, and $\mathbf{I_h}$ are called operator matrices.

\begin{eqnarray}
\left[\mathbf{I_h}\right]_{qj}&=& \Pablo{-} \int h(z_q,\xi_q\rightarrow\hat{\xi})\varphi_j(z_q,\hat{\xi}) d\hat{\xi}\nonumber \\
&=& \Pablo{-} \sum_k h(\xi_q\rightarrow s_k \rightarrow\xi_q)\varphi_j(z_q,s_k) \omega_k
\end{eqnarray}

\Pablo{No hay que borrar el segundo $\xi$ dentro de h, del segundo renglon?}

Here, we define new quadrature points and weights such that $s_k$ exists within the integration boundaries for each row of the integral operator matrix. For \Pablo{the present problem the integration limits are the domain limits.}

\section{Results}

\noindent Choosing the values A=, V=, M= and M= \TODO{no me acuerdo}.
